---
title: "Meteorology"
author: "Sophie Breitbart"
date: "June 15, 2021"
output: html_document
---

# Set up notebook
## Load libraries
```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
library(here)
library(magrittr)
library(tidyverse)
```

## Set strings as factors to false
```{r}
options(stringsAsFactors = FALSE)
```

## Import data
```{r}
weather <-
  read.csv(here::here("./Meteorology/DailyData_OakvilleTwn_2018_2019.csv"),
           header=T,
           na.strings=c("","NA"))
```

## Remove irrelevant data & clean up column names
```{r}
weather %<>%
  dplyr::rename(.,
                "Lat" = 1,
                "Long" = 2,
                "Max.Temp_C" = 10,
                "Min.Temp_C" = 12,
                "Mean.Temp_C" = 14,
                "Total.Precip" = 24) %>%
  dplyr::select(c(1:3, 5:8, 10, 12, 14, 24 ))
```

# Quality control
## Check range of variables
```{r}
boxplot(weather[,8:11], las=2)
lines(c(0,15), c(0,0))
```

## Check for empty values
```{r}
sum(is.na(weather$Max.Temp_C)) # 1 day: 6/18/2018
sum(is.na(weather$Min.Temp_C)) # 1 day: 6/18/2018
sum(is.na(weather$Mean.Temp_C)) # 2 days: 6/18/2018 & 6/19/2018
sum(is.na(weather$Total.Precip)) # 1 day: 6/18/2018

# Since there's only 2 days without full data, remove those days from dataset
weather %<>%
  filter(is.na(weather$Mean.Temp_C) == F)

```

# Aggregate by month or quarter (season)
## Aggregate by month
```{r}
monthly_data <- weather %>% 
  group_by(Year, Month) %>% # group by the month column
  summarise(n=n(), 
            total_precip=sum(Total.Precip), 
            mean_temp=mean(Mean.Temp_C),
            mean_max_temp = mean(Max.Temp_C),
            mean_min_temp = mean(Min.Temp_C)) %T>%
  print(head())

monthly_data$Year <- as.factor(monthly_data$Year)

# Missing full days:
# - 2 days in June 2018
# - This will affect total precipitation data more than other data where means are used
```


## Aggregate by quarter (season)
```{r}

weather %<>%
  mutate(Quarter = case_when(Year == 2018 & Month < 4 ~ 1, 
                             Year == 2018 & Month < 7 ~ 2,
                             Year == 2018 & Month < 10 ~ 3,
                             Year == 2018 & Month < 13 ~ 4,
                             Year == 2019 & Month < 4 ~ 5, 
                             Year == 2019 & Month < 7 ~ 6,
                             Year == 2019 & Month < 10 ~ 7,
                             Year == 2019 & Month < 13 ~ 8) )

quarterly_data <- weather %>% 
  group_by(Quarter) %>% # group by the quarter column
  summarise(n=n(), 
            year = first(Year),
            total_precip=sum(Total.Precip), 
            mean_temp=mean(Mean.Temp_C),
            mean_max_temp = mean(Max.Temp_C),
            mean_min_temp = mean(Min.Temp_C)) %T>%
  print(head())
```

# Analyze by experimental period
## Monthly mean precipitation data
```{r fig.height=3.5, fig.width=9}
# line graph
monthly_data %>%
  ggplot(aes(x = Month,
             y = total_precip,
             color = Year,
             linetype = Year)) +
    geom_line(size = 1)  +
  ylab("Total precipitation (mm)") +
  scale_x_discrete(name ="Month", 
                    limits=c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sept", "Oct", "Nov", "Dec")) +
  ylim(0, 200) +
  scale_color_grey(start = 0.4, end = 0.6)+
  theme_bw()

# export
ggsave(here::here("./Figures_Tables/Meteorology/Monthly_precip_linegraph.png"),
         width = 18, height = 8, units = "cm")



# bar graph
monthly_data %>%
  ggplot(aes(x = Month,
             y = total_precip,
             fill = Year)) +
    geom_bar(position="dodge", stat = "identity")  +
  ylab("Total precipitation (mm)") +
  scale_x_discrete(name ="Month", 
                    limits=c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sept", "Oct", "Nov", "Dec")) +
  ylim(0, 200) +
  scale_fill_grey(start = 0.4, end = 0.6)+
  theme_bw()

# export
ggsave(here::here("./Figures_Tables/Meteorology/Monthly_precip_bargraph.png"),
         width = 18, height = 8, units = "cm")
```


## Monthly mean temperature data
```{r fig.height=3.5, fig.width=9}

# line graph
monthly_data %>%
  ggplot(aes(x = Month,
             y = mean_temp,
             color = Year,
             linetype = Year)) +
    geom_line(size = 1)  +
  ylab("Mean temperature (C)") +
  scale_x_discrete(name ="Month", 
                    limits=c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sept", "Oct", "Nov", "Dec")) +
  ylim(-10, 30) +
  scale_color_grey(start = 0.4, end = 0.6)+
  theme_bw()

# export
ggsave(here::here("./Figures_Tables/Meteorology/Monthly_temp_linegraph.png"),
         width = 18, height = 8, units = "cm")


# bar graph
monthly_data %>%
  ggplot(aes(x = Month,
             y = mean_temp,
             fill = Year)) +
    geom_bar(position="dodge", stat = "identity")  +
  ylab("Mean temperature (C)") +
  scale_x_discrete(name ="Month", 
                    limits=c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sept", "Oct", "Nov", "Dec")) +
  ylim(-10, 30) +
  scale_fill_grey(start = 0.4, end = 0.6)+
  theme_bw()

# export
ggsave(here::here("./Figures_Tables/Meteorology/Monthly_temp_bargraph.png"),
         width = 18, height = 8, units = "cm")
```


# Export tables
```{r}
write.csv(monthly_data, here::here("./Figures_Tables/Meteorology/Monthly_data.csv"), row.names=TRUE)

write.csv(quarterly_data, here::here("./Figures_Tables/Meteorology/Quarterly_data.csv"), row.names=TRUE)
```
